% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{fontawesome}
\usepackage{hyperref}

\begin{document}
    \name{Gabriele Angeletti\\[12pt]} % the \\[12pt] adds a blank line after name
    \begin{resume}
        \section{}
        \faEnvelope~\textbf{angeletti.gabriele@gmail.com} \\[5pt]
        \faGithub~\textbf{\url{https://github.com/gabrieleangeletti}} \\[5pt]
        \faLinkedin~\textbf{\url{https://www.linkedin.com/in/gabriele-angeletti}} \\[5pt]
        \faPhone~\textbf{(+39) 380 148 3213}

        \section{Experience}
            {\bf Senior Software Engineer, } \href{https://tryvital.io}{Vital}
            \hfill Feb 2022 -- Present
            \begin{itemize}
                \item Played a key role as the first full-time engineer outside of leadership. Collaborated closely with founders to establish engineering practices and contribute to the foundational development of the core infrastructure.
                \item Led efforts that successfully scaled the company's user base from 700 to over 1M, handling over 15B individual data points.
            \end{itemize}
        
            {\bf Senior Software Engineer (part-time),} \href{https://larki.com.au/}{Larki}
            \hfill Feb 2021 -- Feb 2022
            \begin{itemize}
                \item Design and develop a system to automatically align Lidar point clouds from a variety of sensors.
                \item Research on 3D object detection/semantic segmentation approaches to extract information from point clouds.
            \end{itemize}

            {\bf Software Engineer,} \href{https://www.lyft.com/self-driving-vehicles/}{Lyft Level 5}
            \hfill Oct 2018 -- Jan 2020\\
            \begin{itemize}
                \item Led the project to develop a distributed data pipeline, efficiently running large-scale Structure From Motion (SfM) on hundreds of millions of images.
                \item Implemented an innovative algorithm for automatic detection and 3D placement of traffic lights in imagery data, increasing the accuracy of point cloud generation.
                \item Designed and implemented dashboards to consistently monitor the quality of SfM point clouds, reducing errors and increasing the reliability of data analysis.
                \item Developed an internal web application capable of visualizing driving patterns in real-time at scale.
            \end{itemize}

            {\bf Research Engineer,} \href{http://www.bluevisionlabs.com}{Blue Vision Labs} \hfill Jan 2018 -- Oct 2018\\
            \begin{itemize}
                \item Design of a data pipeline to automate the testing and evaluation of 3D mapping and localization algorithms.
                \item Work on the cloud infrastructure to run distributed 3D mapping at scale.
                \item Research: test the use of deep learning at different stages of the mapping pipeline to improve quality.
            \end{itemize}

            {\bf Research Engineer intern,} \href{http://www.bluevisionlabs.com}{Blue Vision Labs} \hfill Aug 2017 -- Dec 2017\\
            \begin{itemize}
                \item Research: replacing SIFT with deep learning to improve 2D feature detection.
                \item Design and build a data lake with AWS Redshift to store imagery metadata.
                \item Implementation of algorithms to evaluate the 3D mapping system.
            \end{itemize}

            {\bf Freelancer,} \hfill 2014 -- 2017\\
            Part-time work on different projects during university as a full-stack web developer.

            {\bf Student,} \href{http://www.innovactionlab.org/?lang=en}{InnovAction Lab} \hfill Spring 2013\\
            Entrepreneurship course on how to create a startup and pitch ideas to investors.

        \section{Education}
            Sapienza University of Rome, \hfill 2015 -- 2017 \\
            M.Sc.\ in Engineering in Artificial Intelligence and Robotics, (English Degree) \\
            Final grade 110/110 \\
            Thesis: \textit{Adaptive Deep Learning through Visual Domain Localization \footnote{\url{https://github.com/blackecho/master-thesis}}}

            Sapienza University of Rome, \hfill 2011 -- 2014 \\
            B.Sc.\ in Engineering in Computer Science and Automation, (Italian Degree) \\
            Final grade 106/110 \\
            Thesis: \textit{Statistical analysis of mobile apps reviews to improve users' QoE}

        \section{Technologies}
        \begin{itemize}
            \item \textbf{Programming languages}
            \begin{itemize}
                \item \textbf{Python}: 6 years of experience managing large codebases in dynamic, high-pressure settings.
                \item \textbf{Go}: A year of experience developing diverse microservices.
            \end{itemize}

            \item \textbf{Cloud}
            \begin{itemize}
                \item GCP: extensive experience mainly on BigTable, BigQuery, CloudRun, CloudFunctions, CloudStorage, and IAM.
                \item AWS: extensive experience with key services including Redshift, S3, Lambda, EC2, ECS, and Batch.
            \end{itemize}

            \item \textbf{Data Pipelines and Databases}
            \begin{itemize}
                \item Extensive experience with PostgreSQL, BigTable, and Redshift database systems.
                \item Proficient in Spark, Airflow, and Luigi for data pipeline construction.
            \end{itemize}

            \item \textbf{Front-end development}
            \begin{itemize}
                \item Basic knowledge of React and TypeScript.
            \end{itemize}

            \item \textbf{DevOps}
            \begin{itemize}
                \item Skilled in Docker, Terraform, Pulumi, BuildKite, and GitHub Actions.
            \end{itemize}
        \end{itemize}

        \section{Projects}
        \begin{description}
            \item Deep Learning TensorFlow \footnote{\url{https://github.com/blackecho/Deep-Learning-TensorFlow}}:
                Ready to use implementations of various Deep Learning algorithms using TensorFlow.
        \end{description}

        \section{Publications}
        \begin{description}
            \item G. Angeletti, T. Tommasi, B. Caputo.
                "Adaptive Deep Learning through Visual Domain Localization".
                In: \textit{IEEE International Conference on Robotics and Automation (ICRA)}(2018) \footnote{\url{https://arxiv.org/abs/1802.08833}}
        \end{description}

        \section{Languages}
        \begin{description}
            \item Italian - native speaker.
            \item English - full proficiency with near-native fluency.
            \item French - fluent in speaking and reading, with developing writing abilities.
        \end{description}

        \section{Honors}
        \begin{description}
            \item Ranked 13 / 2189 among Python github users in Italy by \footnote{\url{http://git-awards.com/}} \hfill 2018
            \item Winner of Accenture Digital Hackathon Rome \hfill 2016
            \item NASA International SpaceApps Challenge \hfill 2015\\
                Local winner (Rome) \& Global winner for category Galactic Impact\\
                Project: CROPP---Cultures Risks Observation and Prevention
                Platform\footnote{\url{https://2015.spaceappschallenge.org/award/}}
        \end{description}

        \section{Activities \& Hobbies}
        \begin{description}
        	\item Surfing, scuba diving, climbing, running, hiking.
        \end{description}
    \end{resume}
\end{document}
